%%
%%::::::::::::::::::::::::::::commands
\input{cmd-text}
\input{cmd-math}


%%
%%::::::::::::::::::::::::::::SHELLs
\chapter{SHELL8}
7-Parameter shell formulation with relative displacements as parameterization of
rotations. 

\subitempart{} 
4-noded and 9-noded quad implemented.

\subitempart{} 
Nonlinear stiffness, internal forces and geometry, Large deformation (Piola-Kirchoff II) only.
Consistent Mass matrix implemented, no lumping.

\subitempart{} 
ANS for transverse shear supported in 4/9 noded element

\subitempart{} 
EAS for linear strains through thickness supported in 4/9 noded element.
Can be turned of to obtain 6 parameter shell formulation.

\subitempart{} 
EAS enrichement for constant and linear components of all shell forces supported.
Can be turned on/off separately.

\subitempart{} 
Combined EAS/ANS element can be practically considered locking free.
Element is computationally expensive.

\subitempart{} 
Supports St. Venant-Kirchhoff, Neo Hooke, Ogden, Viscous Ogden material models.
All material models are 3D but storage is element specific.

\subitempart{} 
Supports point, line, area Neumann boundary conditions on mid/top/bottom surface
of shell. Supports FSI, deformation dependent hydrostatic (orthopressure) and 'under water' load cases.

\subitempart{} 
Individual load curves are ignored. Always curve CURVE1 used.

\subitempart{} 
Output of displacements to GID as hex8 or quad4 visualization. Output of shell forces
to gid as quad4 visualization, also in parallel (!).

\subitempart{} 
Supports large deformation self contact in serial/parallel, node-to-segment formulation
with Uszawa type augmented Lagrange multipliers. Not energy conserving.